### 2015-11-03 Assignment III/Abgabe/Assignment3-Ditz_Schroeder-WS15-16.tex
added Abgabe to Assignment III

\section*{Practical Assignment - \textsl{Using BLAT to align 454 reads to the Helicobacter pylori genome}}

>>>>

\section*{Practical Assignment - \textsl{Using BLAT to align 454 reads to the Helicobacter pylori genome}}
The blat algorithm was compiled in a virtual box using bio-linux. The output generated by the blat algorithm was saved as .plt and is attached. The maximal Intron size was set to 50, to limit the ammount of hits. Generally this is a good idea, because introns which are getting to large make no sense in a biological context. The analysis was accomplished by a java program, which is also attached. The program was executed via eclipse and not via the command line. If you want to use it, you might change the path directions in the main class and it should work than. Sadly is the runtime very high and was around 45 mins for the given data set. \\

The complete Data set had 524427 entries. The absolute number of reads, which was be aligned is  437586 or 83 \%. Of these reads 314896 were unique, which are 60\%.
A second part of the task was to figure out how many positions of the H. pylori were left unaligned. From the total number of positions 1691694, 1071574 which is a coverage of 63%.\\
The repeating of sequences can happen very often in different contexts. For example in with noncoding sequence regions or with viral DNA which is stabil incorporated into the genome.
